Expos\'{e}\\ Input Language for Smart Contract API

### 2020-11-08 meeting-notes/20201108-expose-input-language.tex
fine tuning

@@

Or given a contract for index type \lstinline/t/, we'd have an
invocation function
\begin{lstlisting}[language=Caml]
invoke : 't Mtype Tezos.contract -> 't -> result Tezos.apimonad
\end{lstlisting}
with an internal serialization function
\begin{lstlisting}[language=Caml]
serialize : 't Mtype -> 't -> string
\end{lstlisting}
Not sure if deserialization is also needed, but it might be necessary
to decode the current state of a contract. Deserialization may fail
and thus raise an exception.
\begin{lstlisting}[language=Caml]
deserialize : 't Mtype -> string -> 't
\end{lstlisting}
\end{document}

>>>>

\lstset{numbers=none}

@@

Or given a contract for index type \lstinline/t/, we'd have an
invocation function
\begin{lstlisting}[language=Caml]
invoke : 't Mtype Tezos.contract -> 't -> result Tezos.apimonad
\end{lstlisting}
with an internal serialization function
\begin{lstlisting}[language=Caml]
serialize : 't Mtype -> 't -> string
\end{lstlisting}
Not sure if deserialization is also needed, but it might be necessary
to decode the current state of a contract. Deserialization may fail
and thus raise an exception.
\begin{lstlisting}[language=Caml]
deserialize : 't Mtype -> string -> 't
\end{lstlisting}

One can get rid of the \lstinline/Mtype/ datatype by directly
composing serializers in tagless style. I think. But having the type
representation might be more flexible.
\begin{lstlisting}[language=Caml]
s_string : string -> string
s_int : int -> string
s_bool : bool -> string
s_unit : unit -> string
s_list : ('t -> string) -> ('t list -> string)
s_pair : ('l -> string) -> ('r -> string) -> ('l * 'r -> string)
s_option : ('t -> string) -> ('t option -> string)
s_or : ('l -> string) -> ('r -> string) 
     -> ([`Left of 'l | `Right of 'r] -> string)
\end{lstlisting}

Example
\begin{lstlisting}[language=Caml]
mytype = Tor (Tbool, Toption (Tstring))
myserializer = serialize mytype : 
               [`Left of bool | `Right of string option] -> string

tlserializer = s_or s_bool (s_option s_string) :
               [`Left of bool | `Right of string option] -> string
\end{lstlisting}
\end{document}
